\documentclass[12pt,oneside]{report}

\usepackage[nottoc]{tocbibind}


\newcommand{\reporttitle}{Mixed Traffic Simulation for Autonomous Systems in Shared Spaces}
\newcommand{\reportauthor}{Frederik Tobias Hillier}
\newcommand{\reporttype}{Interim Report}
\newcommand{\cid}{01412520}

\newcommand{\supervisor}{Prof Y.K. Demiris}
\newcommand{\supervisorassistant}{Dr X. Zhang}
\newcommand{\secondmarker}{Prof D. Gunduz}


% include files that load packages and define macros
\input{imports/includes} % various packages needed for maths etc.
\input{imports/notation} % short-hand notation and macros


%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% front page
\input{imports/titlepage}

\tableofcontents
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Main document
\chapter{Introduction}
\input{01_Introduction/introduction}


\chapter{Background}

\section{Background Theory}
\input{03_Background/backgroundTheory}

\section{Analysis of Relevant Literature} \label{BackgroundLit}
\input{03_Background/simulatorResearch}

\section{Analysis of Competing Products} \label{AoCP}
\input{03_Background/AnalysisOfCompetingProducts}



\chapter{Implementation}
\input{04_Implementation/implementation}
\section{Future Work} \label{FuturePlanning}
\subsection{Development}
After pedestrians have been added we will need to look at implementing APIs to control them. This should try to follow a similar style to the APIs currently available to control the vehicle. Thereafter we could make minor modifications to the pedestrians so that other mobile robots could be controlled as well. 
\\~\\
The next step would then be to implement the sensing APIs for our new entities. First and foremost, a camera illustrating the pedestrians' point of view would be the most important one,. And once this is done extending it so that it would work for mobile robots as well. 
Following that, we would like to have other kinds of sensors for the mobile robots working. These could for example be ultrasonic and LiDAR. 
\\~\\
When this is done, we will have most of the features we are looking for in the simulator. This will hopefully be done sometime in the middle of March.

\subsection{Evaluation Plan}
\input{05_Evaluation/evaluation}
\pagebreak
\section{Future Timeline} \label{timeline}
\input{04_Implementation/timeline}
\\~\\
When looking at the timeline, it is worth noting that future work might be pushed back if the AirSim development takes longer than anticipated. 
\pagebreak
\section{Extensions}\label{Extensions}
\input{04_Implementation/extensions}

\chapter{Ethical, Legal and Safety Considerations}
\input{06_Considerations/ELS_Plan}


\newpage
\bibliographystyle{IEEEtran} %agsm
\nocite{*}
\bibliography{references}

\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
